\documentclass{article}

\usepackage{graphicx}
\usepackage{hyperref}

\title{MAS ISW Assignment 1}
\date{}
\author{Simon Deussen}

\begin{document}
  \pagenumbering{gobble}
  \maketitle
  \pagenumbering{arabic}

\section*{Task 3: Resources for literature search}
\begin{description}
    \item[Bielefeld Academic Search Engine] 
    Search engine for academic and scientific web resources. Indexes journals, institutional repositories, and releases.
    \href{https://www.base-search.net/}{Link.}
    
    \item[Library Genesis] 
    Search engine for articles, books, journals and magazines. Indexes publicly accessible and 
    user uploaded data. \href{http://libgen.rs/}{Link.}

    \item[WorldCat] OPAC search engine. \href{www.worldcat.org}{Link.}

    \item[ResearchGate] A social network for european scientists. \href{https://www.researchgate.net/}{Link.}
    
    \item[Google Scholar] Googles take for finding scientific and 
    academic articles, books, journals and magazines. 
    \href{https://scholar.google.com/}{Link.}

    \item[Jurn] 
    Enhancement of Google Scholar by a handpicked selection. \href{http://www.jurn.org/#gsc.tab=0}{Link.}
  
    \item[Wolfram Alpha] 
    Knowledge engine, containing infos about all kinds of subjects. \href{https://www.wolframalpha.com/}{Link.}
     
    \item[OpenGreyt]
    Collects bibliographical references to research, dissertations and conference papers mainly produced in europe. \href{http://www.opengrey.eu/}{Link.}
  \end{description}

\section*{Task 4: Collecting articles/books}
\begin{enumerate}
    \item \begin{enumerate}
        \item Tried searching Library Genesis for authors and title - nothing found
        \item Tried searching WorldCat title - found the book in some german libraries but no ebook. \href{https://www.worldcat.org/title/expert-systems-in-the-micro-electronic-age/oclc/6512638}{Link.}
        \href{https://index.ub.rwth-aachen.de/TouchPointClient_touchpoint/singleHit.do?methodToCall=showHit&curPos=1&identifier=2_SOLR_SERVER_1667438747}{Link to Library RWTH Aachen'}
        \item Found it partially by using ISBN (from RWTH Aachen) on DuckDuckGo: \href{https://stacks.stanford.edu/file/druid:tm169ds9492/tm169ds9492.pdf}{Link.}
        But this pdf does not contain the relevant paper.
        \item Found this time the relevant paper using Google Scholar on \href{http://www.shamurai.com/files/Hayes_1979.pdf}{shamurai}
        
        Search term: \textbf{"Mitchie Expert Systems in the Microelectronic Age, Edinburgh Univ. Press."}
        
    \end{enumerate}
    \item \begin{enumerate}
        \item Searched for the title with ResearchGate and directly found it here: 
        \href{https://www.researchgate.net/publication/3802831_Unified_analysis_on_mobility_and_manipulability_of_mobile_manipulators}{Link.}
        Unfortunately it is only accessible after a request. 
        \item Searched for title on LibGen and found it on \href{http://libgen.rs/scimag/10.1109%2Frobot.1999.772525/}{scihub}
        
        Search term: "Unified analysis on mobility and manipulability of mobile manipulators"
    \end{enumerate}

    \item \begin{enumerate}
        \item Searched for the title with LibGen and directly found it here \href{http://library.lol/main/6A6947E0F0669F307D90C679A2D060CB}{Link.}
        
        Search term: \textbf{"Philosophiae Naturalis Principia Mathematica"}
    \end{enumerate}

    \item \begin{enumerate}
        \item Searched for the title with LibGen and directly found it here: \href{https://cloudflare-ipfs.com/ipfs/bafykbzacebosyximsd3u4dnnhftdyq7xyn2lyojmzej4zklcuspyvqb6tcz5w?filename=V.V.%20Fedorov%20-%20Theory%20of%20Optimal%20Experiments-Academic%20Press%20%281972%29.pdf}{Link.}
        
        Search term: \textbf{"V. V. Fedorov. Theory of Optimal Experiments"}
    \end{enumerate}

    \item \begin{enumerate}
        \item Searched for the title with ResearchGate and directly found it here: 
        \href{https://www.researchgate.net/publication/228942691_Active_Learning_Literature_Survey}{Link.}
        Unfortunately it is only accessible after a request. 
        \item Searched for author and title on LibGen and found nothing.
        \item Searched for author and title on Google Scholar and found a link to the University of Wisconsin–Madison with a \href{https://minds.wisconsin.edu/bitstream/handle/1793/60660/TR1648.pdf?sequence=1&isAllowed=y}{download Link.}.
       
        Search Term: \textbf{"Settles, B. (2009) Active Learning Literature Survey"}
    \end{enumerate}
\end{enumerate}
% \bibliography{stuff} https://www.researchgate.net/publication/3902425_Manipulability_analysis_for_mobile_manipulators
% \bibliographystyle{ieeetr}

\end{document}